Covariates analysis of MSBB RNASeq data

### 2015-12-31 code/Rmd/MSSM_RNASeq.Rmd
Minor fix

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Differential expression analysis';
activityDescription = 'Differential expression analysis of MSBB RNASeq samples';

@@

Remove genes that have less than 1 cpm counts in at least 50% of samples.
```{r cpmnormalisation, cache=TRUE}
ind <- intersect(rownames(METADATA), colnames(COUNT))
METADATA <- METADATA[ind,]
COUNT <- COUNT[1:1000, ind]
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT,MIN_GENE_CPM=1, MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
```
### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering, cache=TRUE}
FactorCovariates <- c('TISSUE','Donor','RACE','CDR','CERJ','SEX','NP.1','bbscore','Dx')
ContCovariates <- c('PMI','AOD','PlaqueMean')

@@

# Expression
expr = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsembleIDs')
write.table(expr, file='expression.tsv', sep = '\t', row.names=F, quote=F)
obj = File('expression.tsv', 
           name = 'Voom Adjusted Weighted Residual Expression', 
           parentId = parentId)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)

# Covariates
covar = rownameToFirstColumn(COVARIATES, 'SampleId')
write.table(expr, file='covariates.tsv', sep = '\t', row.names=F, quote=F)
obj = File('covariates.tsv', 
           name = 'Covariates', 
           parentId = parentId)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)
```

>>>>

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = FALSE)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB RNASeq samples';

@@

Remove genes that have less than 1 cpm counts in at least 50% of samples.
```{r cpmnormalisation, cache=TRUE}
ind <- intersect(rownames(METADATA), colnames(COUNT))
METADATA <- METADATA[ind,]
COUNT <- COUNT[, ind]
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT,MIN_GENE_CPM=1, MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
```
### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering, cache=TRUE}
FactorCovariates <- c('TISSUE','Donor','RACE','CDR','CERJ','SEX','NP.1','bbscore','Dx')
ContCovariates <- c('PMI','AOD','PlaqueMean')

@@

# Expression
expr = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsembleIDs')
write.table(expr, file='expression.tsv', sep = '\t', row.names=F, quote=F)
obj = File('expression.tsv', 
           name = 'Voom Adjusted Weighted Residual Expression', 
           parentId = CODE$properties$id)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)

# Covariates
covar = rownameToFirstColumn(COVARIATES, 'SampleId')
write.table(covar, file='covariates.tsv', sep = '\t', row.names=F, quote=F)
obj = File('covariates.tsv', 
           name = 'Covariates', 
           parentId = CODE$properties$id)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)
```
